### 2019-02-14 Sections/economics_of_the_quantum_internet.tex
Econ table

Elements associated with \textsc{Unify} strategies will undergo the quantum utility payoff enhancement,
\begin{align}\label{eq:util_payoff_enh_1}
(f^{(X)}_\mathrm{sc}(n_X),f^{(Y)}_\mathrm{sc}(n_Y)) \underset{\textsc{Unify}}{\longrightarrow} (c_X,c_Y),
\end{align}
where,
\begin{align}\label{eq:util_payoff_enh_2}
c_X &= \frac{n_X}{n_X+n_Y}\cdot f^{(X)}_\mathrm{sc}(n_X+n_Y),\nonumber\\
c_Y &= \frac{n_Y}{n_X+n_Y}\cdot f^{(Y)}_\mathrm{sc}(n_X+n_Y),
\end{align}
from the definition for time-shared compute power given in Def.~\ref{def:time_share_comp_power}.

As before, we can logically generalise the payoff enhancement of a generalised \textsc{Unify} strategy to the multi-player scenario as,
\begin{align}
	f_\mathrm{sc}^{(i)}(n_i) \underset{\textsc{Unify}}{\longrightarrow} \frac{n_i}{\sum_{j=1}^N n_j} \cdot f_\mathrm{sc}^{(i)}\left(\sum_{j=1}^N n_j\right).
\end{align}

Thus, it is evident that the enhancement in \textsc{Unify} strategies is highly dependent on:
\begin{itemize}
	\item The total number of qubits held between the players,
		\begin{align}
			n_\mathrm{total} = \sum_j n_j.
		\end{align}
	\item The proportion of the qubits held by each player,
		\begin{align}
			r_i = \frac{n_i}{\sum_{j=1}^N n_j}.
		\end{align}
	\item The respective algorithms to which the computational resources are being applied by each player, which influence the player-specific subjective scaling functions, $f^{(i)}_\mathrm{sc}$, independently.
\end{itemize}

@@

	\begin{flushleft}Time-share computational power (Sec.~\ref{sec:arb_free_time_share})\end{flushleft} & \[c_n=n \cdot \chi_\mathrm{sc}(n_\mathrm{global})

@@

	\begin{flushleft}Cooperative payoff enhancement (Sec.~\ref{sec:coop_enh})\end{flushleft} & \[c_X = \frac{n_X\cdot f^X_\mathrm{sc}(n_X+n_Y)}{n_X+n_Y} \] & \[ n_X\] & \[ n_X(n_X+n_Y)^{p-1} \] & \[ \frac{n_X\cdot e^{n_X+n_Y}}{n_X+n_Y}\] \\

>>>>

Elements associated with \textsc{Unify} strategies will undergo the quantum utility payoff enhancement,
\begin{align}\label{eq:util_payoff_enh_1}
(f^{(X)}_\mathrm{sc}(n_X),f^{(Y)}_\mathrm{sc}(n_Y)) \underset{\textsc{Unify}}{\longrightarrow} (c_X,c_Y),
\end{align}
where,
\begin{align}\label{eq:util_payoff_enh_2}
c_X &= n_X \cdot \chi^{(X)}_\mathrm{sc}(n_X+n_Y),\nonumber\\
c_Y &= n_Y \cdot \chi^{(Y)}_\mathrm{sc}(n_X+n_Y),
\end{align}
from the definition for time-shared compute power given in Def.~\ref{def:time_share_comp_power}.

As before, we can logically generalise the payoff enhancement of a generalised \textsc{Unify} strategy to the multi-player scenario as,
\begin{align}
	f_\mathrm{sc}^{(i)}(n_i) \underset{\textsc{Unify}}{\longrightarrow} n_i \cdot \chi_\mathrm{sc}^{(i)}(n_\mathrm{global}).
\end{align}

Thus, it is evident that the enhancement in \textsc{Unify} strategies is highly dependent on:
\begin{itemize}
	\item The total number of qubits held between the players,
		\begin{align}
			n_\mathrm{global} = \sum_{j=1}^N n_j.
		\end{align}
	\item The proportion of the qubits held by each player,
		\begin{align}
			r_i = \frac{n_i}{\sum_{j=1}^N n_j}.
		\end{align}
	\item The respective algorithms to which the computational resources are being applied by each player, which influence the player-specific subjective scaling functions, $f^{(i)}_\mathrm{sc}$, independently.
\end{itemize}

@@

	\begin{flushleft}Time-share computational power (Sec.~\ref{sec:arb_free_time_share}); Cooperative payoff enhancement (Sec.~\ref{sec:coop_enh})\end{flushleft} & \[c_n=n \cdot \chi_\mathrm{sc}(n_\mathrm{global})

@@
